\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
Added DOI
Revised

\url{https://github.com/ncsu-swat/bugsindlls}\\

@@

\url{https://www.youtube.com/watch?v=NslNWrULT1c}\\
% \Fix{Upload to YouTube with voiceover and add link here, archive 
% the tool at zenodo}

@@

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, creation of docker container associated with the tool
done\Fix{ask gpt to revise/polish the text} with the script
\CodeIn{install\_freefuzz\_docker.sh}.  Then, an example bug\Fix{I
  don't understand ``example bug''. bugs in this version, no??!!} that
is reproducible with the library version provided as an input is run
as a sanity check.  Then, the preprocessing script
(\CodeIn{preprocess.py}) is executed to extract error types and buggy
APIs for a specific library vesion and the environment inside the
docker container of the tool is updated to match the library version
passed as an input and the fuzzing tool runs inside the
enviroment. After the execution is complete, the script finally runs a
postprocessing script (\CodeIn{postprocess.py}) to check the execution
log against the ground truth to determine if the bugs were reproduced
or not.

>>>>

\url{https://github.com/ncsu-swat/bugsindlls}

@@

\url{https://www.youtube.com/watch?v=NslNWrULT1c}

The archived version at Zenodo is available with this DOI:

\url{https://doi.org/10.5281/zenodo.15064163}\\

% \Fix{Upload to YouTube with voiceover and add link here, archive 
% the tool at zenodo}

@@

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install_freefuzz_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.
